Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2021-01-11 eg6-letters/long-paper/prc-dvcshelium.tex
Add the 2nd round of AdHoc for long paper
Changes from last round of ad hoc committee comments

CLAS \cite{Mecking:2003zu} was installed in the hall-B of the JLab continuous electron beam 
accelerator facility (CEBAF). CLAS was specifically designed to study the multi-particles final states
that cannot be observed conveniently with arm spectrometers. Its historic use to measure DVCS in many different 
configurations made it an ideal place for this new DVCS measurement. CLAS was composed of six identical radial 
sectors separated by coils of toroidal magnets, with each sector made of four detectors 
as shown in Fig. \ref{fig:CLAS}. Three regions of drift chambers \cite{Mestayer:2000we} 
were placed between the torus magnet to reconstruct the charged particles' tracks and 
calculate their momentum. An array of scintillators was placed behind the drift chambers to measure 
a precise time for each track and perform time-of-flight measurement 
\cite{Smith:1999ii}. These detectors covered the polar angle from 8 to 142 degrees. 
In the forward region, from 8 to 45 degree, these two detectors were complemented with 
Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
important for electron identification and photon detection.

@@

We show in Fig.~\ref{fig:cont_yield} the $\pi^0$ contamination for the $-t$ bins, where it varies
the most from one bin to another. The study
shows 2 to 4\% contamination in the coherent channel and 3 to 17\% in the incoherent
channel. To make the correction on the DVCS BSA, we assume that
the exclusive $\pi^0$ production has no such asymmetry. This has been checked with the exclusive 
$\pi^0$ production data, for which no significant level of BSA was measured.

\begin{figure}[tbp]
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_Coh_t.pdf}
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_InCoh_t.pdf}
\caption{The coherent (left) and incoherent (right) $\pi^{0}$ 
contamination estimated in the DVCS events as a function of the 
transferred momentum squared -$t$ and integrated over the kinematical 
variables $Q^2$, $x_B$, and $\phi$.}
\label{fig:cont_yield}
\end{figure}

@@

To evaluate the systematic error of the measurement, we performed several specialized studies. We 
evaluated the impact of changing the exclusivity selection cuts by varying them from 1 to 5 $\sigma$. 
We evaluated the impact of changing the binning in $\phi$ on the extraction of the beam-spin asymmetry
at 90°. The precision with which we know the beam polarization is estimated based on the spread 
of its measurements during the complete run period. We also checked different methods to make the 
simulation of the exclusive $\pi^0$ production and accounted for a possible undetected 
asymmetry in its signal to evaluate the 
possible bias introduced by this correction. As radiative corrections are expected to be small
for this process, we did not apply them, but associated an error of their expected value.
These uncertainties are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
evaluated values. They are added quadratically for the total systematic error presented in the results.

>>>>

CLAS \cite{Mecking:2003zu} was installed in the hall-B of the JLab continuous electron beam 
accelerator facility (CEBAF). CLAS was specifically designed to study the multi-particles 
final states that cannot be observed conveniently with arm spectrometers. It was naturally 
well-suited for measuring DVCS, and several DVCS experiments were successfully conducted 
before this experiment using multiple different configurations. CLAS was composed of six identical radial 
sectors separated by coils of toroidal magnets, with each sector made of four detectors 
as shown in Fig. \ref{fig:CLAS}. Three regions of drift chambers \cite{Mestayer:2000we} 
were placed between the torus magnet to reconstruct the charged particles' tracks and 
calculate their momentum. An array of scintillators was placed behind the drift chambers to measure 
a precise time for each track and perform time-of-flight measurement 
\cite{Smith:1999ii}. These detectors covered the polar angle from 8 to 142 degrees. 
In the forward region, from 8 to 45 degree, these two detectors were complemented with 
Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
important for electron identification and photon detection.

@@

We show in Fig.~\ref{fig:cont_yield} the $\pi^0$ contamination for the $-t$ bins, where it varies
the most from one bin to another. The study
shows 2 to 4\% contamination in the coherent channel and 3 to 17\% in the incoherent
channel. After subtracting this contamination, we make no further correction to 
the DVCS BSA, \textit{i.e}., we assume the exclusive $\pi^0$ production has no such 
asymmetry in either the coherent or incoherent channels. Our own exclusive $\pi^0$ 
data rules out any BSA above approximately 10\%, a level which would have an 
insignificant effect on our results given the small amount of contamination.

\begin{figure}[tbp]
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_Coh_t.pdf}
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_InCoh_t.pdf}
\caption{The estimated coherent (left) and incoherent (right) $\pi^{0}$ 
contamination fraction in the DVCS events as a function of the 
transferred momentum squared -$t$ and integrated over the kinematical 
variables $Q^2$, $x_B$, and $\phi$.}
\label{fig:cont_yield}
\end{figure}

@@

To evaluate the systematic error of the measurement, we performed several specialized studies. We 
evaluated the impact of changing the exclusivity selection cuts by varying them from 1 to 5 $\sigma$. 
We evaluated the impact of changing the binning in $\phi$ on the extraction of the beam-spin asymmetry
at 90°. The precision with which we know the beam polarization is estimated based on the spread 
of its measurements during the complete run period. We studied how different methods of
simulating the exclusive $\pi^0$ production affected the single-photon background and
further estimated how much bias could arise from an undetected BSA in the process. As 
radiative corrections are expected to be small
for this process, we did not apply them, but associated an error of their expected value.
These uncertainties are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
evaluated values. They are added quadratically for the total systematic error presented in the results.
